Localization properties, observable character and computational reliability of the linear response in open systems

### 2018-07-09 AnalyticStructure_main.tex
hello

\begin{abstract}
We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems. We show that optical excitations of energy below the LR ionization potential 
behave as observable, localized quantities, that can be computationally calculated with high precision, provided an adequate level of completeness.
Above this energy threshold, the analytic structure of the susceptibility functional might be separated in two sectors: one can still be described in terms of observable excitation 
with discrete energies, that can be captured within computational setups tailored for localized states. However such excitations are embedded in a continuum of excited states 
that, on the contrary, behave as plane waves and cannot be described efficiently by the same computational techniques. Such excitations do not exhibit observable features and 
\emph{cannot} be considered as poles of the dynamical polarizability. Nonetheless, the contribution of such continuum of excitation reveals to be of paramount importance even 
for expressing LR quantities in the infrared regime like for example static polarizability.
This is particularly evident for small molecules; we show how these considerations might be influenced by the size of molecular system.
We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
in any discretization scheme.  This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
unoccupied subspace.
\end{abstract}

>>>>

\begin{abstract}
A reliable procedure for the analysis of a system within the framework of the linear response should include
the study of the conditions under which numerical convergence of the results can be achieved. 
Such considerations are important not only for reproducibility of the results among different computer codes 
employing diverse formalisms, but also in view of providing a deeper understanding on the impact of models' 
approximations on the scientific outcomes of the simulation.

We discuss these aspects in the context of linear response treatment of molecular systems. 
By analysing simple case-studies with a highly complete numerical formalism, 
we explore the interplay between locality of the perturbed wavefunctions and the 
numerical convergence of observable quantities. We identify some convergence indicators and discuss under which regimes they might be employed. This will enable us to draw some considerations on the analytic structure of the linear susceptivity for open systems and on the potential convergence issues that might arise in a given computational setup.

We believe that such discussion could provide useful considerations and perspectives for the design of a effective approaches for the study of molecular excitations in realistic conditions.

We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems. We show that optical excitations of energy below the LR ionization potential 
behave as observable, localized quantities, that can be computationally calculated with high precision, provided an adequate level of completeness.
Above this energy threshold, the analytic structure of the susceptibility functional might be separated in two sectors: one can still be described in terms of observable excitation 
with discrete energies, that can be captured within computational setups tailored for localized states. However such excitations are embedded in a continuum of excited states 
that, on the contrary, behave as plane waves and cannot be described efficiently by the same computational techniques. Such excitations do not exhibit observable features and 
\emph{cannot} be considered as poles of the dynamical polarizability. Nonetheless, the contribution of such continuum of excitation reveals to be of paramount importance even 
for expressing LR quantities in the infrared regime like for example static polarizability.
This is particularly evident for small molecules; we show how these considerations might be influenced by the size of molecular system.
We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
in any discretization scheme.  This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
unoccupied subspace.
\end{abstract}
